---
title: Hatetracker
output:
  github_document: default
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/davidski/hatetracker.svg?branch=master)](https://travis-ci.org/davidski/hatetracker)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/davidski/hatetracker?branch=master&svg=true)](https://ci.appveyor.com/project/davidski/hatetracker)
[![Coverage Status](https://img.shields.io/codecov/c/github/davidski/hatetracker/master.svg)](https://codecov.io/github/davidski/hatetracker?branch=master)
 
This is an R interface to the SPLC [hatetracker.io](https://hatetracker.io) project.

The data goes back to August 2016.

## Installation

Hatetracker is not on CRAN. Installation from GitHub is simplest via the 
`devtools` package:

`devtools::install_github("davidski/hatetracker")`

## Thanks

- This is an unofficial interface to the hatetracker API. Please be kind to 
the API and consider making a tax-deductible 
[donation](https://donate.splcenter.org/sslpage.aspx?pid=463) to the critically 
important work the SPLC carries out.
- Cheers to @hrbrmstr for his countless packages. Darksky and friends were the 
motivators my creating this interface with a valuable web service.

## Usage

Load the `hatetracker` library and some supporting tooling.

```{r load_libraries, message=FALSE, warning=FALSE}
library(hatetracker)
library(tidyverse)
library(extrafont)
```

Fetch the trending hashtags used in the alt-right community for a specific 
day. The data is returned as a nested dataframe for each trending tag, 
including the total number of times mentioned. The nested timeframe includes 
a z-score normalized trend for the number of mentions at 30 minute intervals 
throughout the requested date range.

```{r fetch_trends}
charlottesville <- as.Date("2017-08-13")
dat <- get_hatetracker_activity(charlottesville + 1)
dat
```

Basic plotting of the activity.

```{r basic_plot, fig.height=12, fig.width= 10}
dat %>% mutate(title = forcats::as_factor(title)) %>% 
  tidyr::unnest() %>% mutate(datetime = as.POSIXct(name, tz = "utc")) %>% 
  ggplot(., aes(x = datetime, y = y)) + geom_col(fill = "orange") + 
  geom_hline(yintercept = 0) +
  #facet_wrap(~title, ncol = 1, strip.position = "left") +
  facet_grid(title ~ .) +
  hrbrthemes::theme_ipsum(grid = "") + 
  theme(strip.text.y = element_text(size = 12, angle = 0, hjust = 0)) +
  labs(title = "Top Hashtags Used by Alt-Right Twitter Accounts", 
       subtitle = "Day after the Charlottesville attack",
       caption = "Source: hatetracker.io",
       y = "Z-Score", x = NULL)
```

We can also look at historical mentions of specific tags. In this case, the 
`#charlottesville` tag.

```{r}
historical <- get_hatetracker_activity2(charlottesville  - 7, charlottesville + 7)
char_hashtag <- historical[[1, "timeline"]]
char_hashtag
```

```{r}
char_hashtag$attack <- as.Date(char_hashtag$date) == charlottesville
ggplot(char_hashtag, aes(date, z_score)) + 
  geom_col(aes(fill = attack)) +
  scale_fill_manual(values = c("orange", "red"), guide = FALSE) + 
  labs(x = NULL, y = "Z-Score", 
       title = "Use of Charlottesville Hashtag by Alt-Right Twitter Users", 
       subtitle = "Week preeceding and following the Chartlottsville attack",
       caption = "Source: hatetracker.io") +
  hrbrthemes::theme_ipsum(grid = "")
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

## License

The [MIT License](LICENSE) applies.
