---
output:
  github_document: default
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/davidski/hatetracker.svg?branch=master)](https://travis-ci.org/davidski/hatetracker)
 
This is an R interface to the SPLC hatetracker.io project.

The data goes back to August 2016.

## Installation

`devtools::install_github("davidski/hatetracker")`


## Thanks

This is an unofficial interface to the hatetracker API. Please be kind to 
the API and consdier donating to the critically important work the SPLC 
carries out.

```{r example}
## basic example code
library(hatetracker)
library(tidyverse)
library(extrafont)
dat <- get_hatetracker_activity("2017-11-25")
dat
```
```{r}
dat %>% mutate(title = forcats::as_factor(title)) %>% 
  tidyr::unnest() %>% mutate(datetime = as.POSIXct(name, tz = "utc")) %>% 
  ggplot(., aes(x = datetime, y = y)) + geom_col() + 
  #facet_wrap(~title, ncol = 1, strip.position = "left") +
  facet_wrap(~title) +
  hrbrthemes::theme_ipsum(grid = "", axis = "x")
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
